---
title: "Multivariate Statistics"
output: html_document
---

```{r setup, include = FALSE, cache = FALSE}
knitr::opts_chunk$set(error = TRUE, comment = NA, warnings = FALSE, errors = FALSE, messages = FALSE, tidy = FALSE, echo = FALSE)
```

The following are all *free* books, available to read online:

- Modern Dive: http://moderndive.com
- R for Data Science: http://r4ds.had.co.nz
- Fundamentals of Data Visualization: http://serialmentor.com/dataviz/
- Data Visualization: A Practical Introduction: http://socviz.co

## Slide Decks & Reading {.tabset}

### 01: Principal Component Analysis

```{r}
knitr::include_url("slides_multivariate_statistics/01-pca.html")
```

- [Presentation](slides_multivariate_statistics/01-pca.html)

### 02: Exploratory Factor Analysis

```{r}
knitr::include_url("slides_multivariate_statistics/02-slides.html")
```


### 03: Confirmatory Factor Analysis

```{r}
knitr::include_url("slides_multivariate_statistics/03-slides.html")
```

### 04: Structural Equation Models

```{r}
knitr::include_url("slides_multivariate_statistics/04-slides.html")
```

### 05: Canonical Correlation Analysis

```{r}
knitr::include_url("slides_multivariate_statistics/06-slides_xaringan.html")
```

### 06: Correspondence analysis

```{r}
knitr::include_url("slides_multivariate_statistics/06-slides_blogdown.html")
```

### 07: Multidimensional scaling

```{r}
knitr::include_url("slides_multivariate_statistics/07-prework-slides_blogdown.html")
```